\textcolor{blue}{A gradient-based optimization method for motion planning}$^{1}$

### 2016-01-18 paper.tex
Start adding new images-results, change Jacobian notation

% Math shortcuts :
\newcommand\real{\mathbb{R}}
\newcommand\p{\mathbf{p}}
\newcommand\gT{\tilde{g}^T}
\newcommand\g{\tilde{g}}
\newcommand\CS{\mathcal{C}}
\newcommand\dimCS{n_\mathbf{C}}
\newcommand\body{{\cal B}}
\newcommand\Sone{\mathbf{S}^1}
\newcommand\Sthree{\mathbf{S}^3}
\newcommand\conf{\mathbf{q}}
\newcommand\xx{\mathbf{x}} % \x already defined in the class
\newcommand\cost{C}
\newcommand\weight{W}
\newcommand\translation{\mathbf{t}}
%\newcommand\tcolli{t_{coll\ i}}
\newcommand\tcolli{\kappa_i}
\newcommand\po{\mathbf{P}}
\newcommand\Jf{{J_f}}
\newcommand\kernel{\mbox{Ker }}
\newcommand\U{\mathbf{u}}

@@

\textcolor{blue}{The constraint function is noted $f$}. Let us assume that at iteration $i$, $j$ constraints have been inserted before the current iteration. 
These constraints are stored as lines of a Jacobian matrix as follows:
$$
\Jf_{i} = \left(\begin{array}{c}L_1 \\ \vdots \\ L_j\end{array}\right)
$$
where the step $\p_i$ is constrained to be in the kernel of $\Jf_{i}$ as follows:
$$
\Jf_{i} \, \p_i = 0
$$

@@

In the collision-configuration $\xx_{i+1}(\tcolli)$, let $\po_c\in \real^3$ be a 
contact point expressed in the global frame 
(Figure~\ref{contact-points} left).
\textcolor{blue}{
In any configuration $\conf$, let 
$\po_j^l(\conf)$ be the coordinates in the frame of $\body_l$ of $\po_c$ expressed the frame of $\body_j$.
Let $M_1(\conf) \in SE(3)$ (resp. $M_2(\conf) \in SE(3)$) denote the homogeneous transformation 
between frames of $\body_1$ (resp. $\body_2$) and the global frame.
Thus, $\po_2^1(\conf) = M_{1}^{-1} (\conf) M_2 (\conf)$.
}

@@

Let $f$ be the function defined from $\CS^{wp}$ to $\real$ by:
$$
f (\xx) = g(\xx (\tcolli))
$$
The constraint is defined for any path $\xx$ by:
\begin {equation}\label{eq:new-constraint}
f(\xx) - f(\xx_{i}) = 0.
\end {equation}
This constraint forces the configuration $\xx (\tcolli)$ to keep the same projection on $\mathbf{u}$ as in $\xx_i (\tcolli)$. Since this constraint is 
non-linear, we linearize it around $\xx_{i}$: 
$$
\frac{\partial f}{\partial \xx}(\xx_i)(\xx - \xx_i) = 0
$$
The linearization step is described in a further 
section. Then, a line is added in the constraint Jacobian matrix (function 
\texttt{addCollisionConstraint}), and the constraint 
Jacobian becomes:
\begin {align*}
\Jf_{i+1} &= \left(\begin{array}{c}L_1 \\ \vdots \\ L_{j+1}\end{array}\right)\ \mbox {with}\\
L_{j+1} &= \frac{\partial f}{\partial \xx}(\xx_i)
\end{align*}

@@

\begin{figure}
	\centering
	\includegraphics[width=15.8cm]{convergence-diagram.pdf}
	\caption{\textcolor{blue}{Considering a trajectory 
	$\conf (t) = (\xx_{Free} + t\, \alpha \p)(\kappa)$ 
	with $\xx_{Coll} = \xx_{Free} + \alpha\p$ ($\xx_{Free}$, $\xx_{Coll}$, $\p$ 
	and $\kappa$ resp. collision-free path, in-collision path, iteration step 
	and collision-abcissa).
	The trajectory is represented in the configuration space (left) and in the 
	workspace with the colliding bodies (right).}
	Note that a case with 
	$(\dot{\po_2}(\xx_{Free})|\mathbf{u})=0$ is considered, so $\p$ already complies 
	with the constraint that should be added if no redundancy was tracked. Therefore, 
	Algorithm~\ref{algo:solveRedundant} will produce one intermediate step
	$\xx$ (gray path and clear bodies). $\xx$ is collision-free and 
	$(\dot{\po_2}(\xx)|\mathbf{u})\neq 0$ so the redundancy is solved, 
	returning the new constraint.}
	\label{fig:convergence-diagram}
\end{figure}

@@

\subsection{From 2D basic examples...}

@@

@@

@@

\begin{figure}
	\centering
	\subfigure[Double-arm]{
		\includegraphics[width=6.5cm,height=5.5cm]{ur2_orth_constr_results.png}
		\label{fig:trajectories:double_arm}
	}
	\subfigure[Freeflyer-puzzle]{
		\includegraphics[width=6.5cm,height=5.5cm]{puzzle_orth_constr_results.png}
		\label{fig:trajectories:puzzle}
	}
	\subfigure[PR2-in-kitchen-1]{
		\includegraphics[width=6.5cm,height=5.5cm]{pr2-kitchen1_orth_constr_results.png}
		\label{fig:trajectories:kitchen1}
	}
	\subfigure[UR5-with-spheres]{
		\includegraphics[width=6.5cm,height=5.5cm]{ur5-spheres_orth_constr_results.png}
		\label{fig:trajectories:ur5}
	}
	\subfigure[PR2-in-kitchen-2]{
		\includegraphics[width=6.5cm,height=5.5cm]{pr2_kitchen2_orth_constr_results.png}
		\label{fig:trajectories:kitchen2}
	}
	\subfigure[Baxter-in-office]{
		\includegraphics[width=6.5cm,height=5.5cm]{baxter_orth_constr_results.png}
		\label{fig:trajectories:baxter}
	}
  \caption{Trajectories of end-effectors, mobile bases or centers along the 
  different paths: the initial path is represented in red, the RS optimized path in 
  blue and the GB optimized path in green. The full robots 
  motions can also be visualized in the joined video. The trajectories comparison 
  highlights the optimization success of our method, which manages to deliver a 
  shorter or similar path compared to RS output}
  \label{fig:trajectories}
\end{figure}

>>>>

% Math shortcuts :
\newcommand\real{\mathbb{R}}
\newcommand\p{\mathbf{p}}
\newcommand\gT{\tilde{g}^T}
\newcommand\g{\tilde{g}}
\newcommand\CS{\mathcal{C}}
\newcommand\dimCS{n_\mathbf{C}}
\newcommand\body{{\cal B}}
\newcommand\Sone{\mathbf{S}^1}
\newcommand\Sthree{\mathbf{S}^3}
\newcommand\conf{\mathbf{q}}
\newcommand\xx{\mathbf{x}} % \x already defined in the class
\newcommand\cost{C}
\newcommand\weight{W}
\newcommand\translation{\mathbf{t}}
%\newcommand\tcolli{t_{coll\ i}}
\newcommand\tcolli{\kappa_i}
\newcommand\po{\mathbf{P}}
\newcommand\Jf{\Phi}
\newcommand\kernel{\mbox{Ker }}
\newcommand\U{\mathbf{u}}

@@

Let us assume that at iteration $i$, $j$ \textcolor{blue}{linear} constraints have been inserted before the current iteration. 
These constraints are stored as lines of a matrix as follows:
$$
\Jf_{i} = \left(\begin{array}{c}L_1 \\ \vdots \\ L_j\end{array}\right)
$$
where the step $\p_i$ is constrained to be in the kernel of $\Jf_{i}$ as follows:
$$
\Jf_{i} \, \p_i = 0
$$
\textcolor{blue}{These linear constraints are built from the linearization of a differentiable function $f$, which will be detailed in the following section.}

@@

In the collision-configuration $\xx_{i+1}(\tcolli)$, let $\po_c\in \real^3$ be a 
contact point expressed in the global frame 
(Figure~\ref{contact-points} left).
\textcolor{blue}{
In any configuration $\conf$, let 
$\po_j^l(\conf)$ be the coordinates in the frame of $\body_l$ of $\po_c$ expressed the frame of $\body_j$.
Let $M_1(\conf) \in SE(3)$ (respectively $M_2(\conf) \in SE(3)$) denote the homogeneous transformation 
between frames of $\body_1$ (respectively $\body_2$) and the global frame.
Thus, $\po_2^1(\conf) = M_{1}^{-1} (\conf) M_2 (\conf)$.
}

@@

Let $f$ be the function defined from $\CS^{wp}$ to $\real$ by:
$$
f (\xx) = g(\xx (\tcolli))
$$
The constraint is defined for any path $\xx$ by:
\begin {equation}\label{eq:new-constraint}
f(\xx) - f(\xx_{i}) = 0.
\end {equation}
This constraint forces the configuration $\xx (\tcolli)$ to keep the same projection on $\mathbf{u}$ as in $\xx_i (\tcolli)$. Since this constraint is 
non-linear, we linearize it around $\xx_{i}$: 
$$
\frac{\partial f}{\partial \xx}(\xx_i)(\xx - \xx_i) = 0
$$
The linearization step is described in the following 
section. Then, a line is added in the constraint Jacobian matrix $\Jf_i$:
\begin {align*}
\Jf_{i+1} &= \left(\begin{array}{c}L_1 \\ \vdots \\ L_{j+1}\end{array}\right)\ \mbox {with}\\
L_{j+1} &= \frac{\partial f}{\partial \xx}(\xx_i)
\end{align*}
\textcolor{blue}{This step is denoted by the function \texttt{addCollisionConstraint}}.

@@

\begin{figure}
	\centering
	\includegraphics[width=15.8cm]{convergence-diagram.pdf}
	\caption{\textcolor{blue}{Considering a trajectory 
	$\conf (t) = (\xx_{Free} + t\, \alpha \p)(\kappa)$ 
	with $\xx_{Coll} = \xx_{Free} + \alpha\p$ ($\xx_{Free}$, $\xx_{Coll}$, $\p$ 
	and $\kappa$ respectively collision-free path, in-collision path, iteration step 
	and collision-abcissa).
	The trajectory is represented in the configuration space (left) and in the 
	workspace with the colliding bodies (right).}
	Note that a case with 
	$(\dot{\po_2}(\xx_{Free})|\mathbf{u})=0$ is considered, so $\p$ already complies 
	with the constraint that should be added if no redundancy was tracked. Therefore, 
	Algorithm~\ref{algo:solveRedundant} will produce one intermediate step
	$\xx$ (gray path and clear bodies). $\xx$ is collision-free and 
	$(\dot{\po_2}(\xx)|\mathbf{u})\neq 0$ so the redundancy is solved, 
	returning the new constraint.}
	\label{fig:convergence-diagram}
\end{figure}

@@

\subsection{From 2D basic examples}

@@

\begin{figure}[H]
	\centering
	\subfigure[Double-arm]{
		\includegraphics[width=6.5cm,height=5.5cm]{2Darm_comparison_alphaInit.png}
		\label{fig:remainingLengthAlphaInit:double_arm}
	}
	\subfigure[Double-arm]{
		\includegraphics[width=6.5cm,height=5.5cm]{2Darm_comparison_alphaInit.png}
		\label{fig:remainingLengthAlphaInit:double_arm}
	}
  \caption{Influence of $\alpha_{init}$.}
  \label{fig:remainingLengthAlphaInit}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\subfigure[Double-arm]{
		\includegraphics[width=6.5cm,height=5.5cm]{ur2_comparison_RS_PRS_GB_sd.png}
		\label{fig:remainingLengthComp:double_arm}
	}
	\subfigure[PR2-crossing-arms]{
		\includegraphics[width=6.5cm,height=5.5cm]{PR2alone_comparison_RS_PRS_GB_sd.png}
		\label{fig:remainingLengthComp:pr2alone}
	}
  \caption{Performance comparison between the three optimizers.}
  \label{fig:remainingLength}
\end{figure}

@@

\begin{figure}
	\centering
	\subfigure[Double-arm]{
		\includegraphics[width=6.5cm,height=5.5cm]{ur2_orth_constr_results.png}
		\label{fig:trajectories:double_arm}
	}
	\subfigure[Freeflyer-puzzle]{
		\includegraphics[width=6.5cm,height=5.5cm]{puzzle_orth_constr_results.png}
		\label{fig:trajectories:puzzle}
	}
	\subfigure[PR2-in-kitchen-1]{
		\includegraphics[width=6.5cm,height=5.5cm]{pr2-kitchen1_orth_constr_results.png}
		\label{fig:trajectories:kitchen1}
	}
	\subfigure[UR5-with-spheres]{
		\includegraphics[width=6.5cm,height=5.5cm]{ur5-spheres_orth_constr_results.png}
		\label{fig:trajectories:ur5}
	}
	\subfigure[PR2-in-kitchen-2]{
		\includegraphics[width=6.5cm,height=5.5cm]{pr2_kitchen2_orth_constr_results.png}
		\label{fig:trajectories:kitchen2}
	}
	\subfigure[Baxter-in-office]{
		\includegraphics[width=6.5cm,height=5.5cm]{baxter_orth_constr_results.png}
		\label{fig:trajectories:baxter}
	}
  \caption{Trajectories of end-effectors, mobile bases or centers along the 
  different paths: the initial path is represented in red, the RS optimized path in 
  blue and the GB optimized path in green. The full robots 
  motions can also be visualized in the joined video. The trajectories comparison 
  highlights the optimization success of our method, which manages to deliver a 
  shorter or similar path compared to RS output.}
  \label{fig:trajectories}
\end{figure}
